### 2019-02-11 tex_v2/manuscript.tex
all but conclusions and methods

%This study demonstrates: (1) there are 2 microstructural modifications to the composite profile of the cuticle of the rostral apex that would enhance cuticular flexibility, present in all examined species, and likely across the genus (2) thickness of the encocuticle is directly proportional to the maximum tensile force sustained in tension, to the exclusion of the exocuticle, (3) the tensile strenth of the snout varies across the length of the head and is inversely proportional to exo/endocuticle ratio, such that the more flexible areas are also stronger under tension, (4) young's modulus is higher for longer snouts, reflecting increased reinforcement at the base of the snout, likely to prevent bucking fracture at the base, (5) because of the modifications to the cuticle of the rostral apex (which result in all of these changes to the mechanical properties of the snout), bending appears to be viscoelastic/elastic, with a relatively low risk of breakage during the lifetime of the beetle, (6) when the rostrum does fail, crack initiation appears to take place in the exocuticle-rich gular sutures, which would be under tension during the drilling behavior in the live insect.

@@

%-------------------------------------------------------------------------------
%introduction - nature materials requires that introduction is given NO SECTION HEADER, 500 words
}	
\section*{Introduction} \info{650 words, reduce to 600 or less in revisions, structure of argument/narrative is good}
%Intro outline - 500 word maximum
%	Paragraph 1 - Cuticle of beetles
%	Paragraph 2 - Weevils and behavior
%	Paragraph 3 - modified cuticle in curculio
%	Paragraph 4 - study objectives
%	Paragraph 5 - short segue/ signposting
	{The exoskeleton of Coleoptera (beetles) is a hierarchically-structured fibrous composite characterized by variously arranged \textalpha-chitin (N-acetylglucosamine) nanofibrils embedded in a heterogeneous protein matrix.
	Although \textalpha-chitin is brittle and strongly anisotropic\unsure{give some numbers here}, beetle cuticle is simultaneously rigid and tough due to its uniquely layered microstructure\unsure{give more numbers here}.
	Beetle cuticle is divided into two structurally and mechanically distinct regions, the (outer) exocuticle and (inner) endocuticle.
	The exocuticle is characterized by a transversely-isotropic helicoidal structure that is comparatively rigid (though brittle) and has been the subject of numerous prior studies\unsure{numbers and refs}.
	By contrast, the endocuticle of beetles is comprised of large, aligned bundles (macrofibers) of chitin that are strongly anisotropic\unsure{numbers again}.
	Arranged in unidirectional laminae, the macrofibers improve cuticle toughness by inhibiting crack formation and propagation between successive plies \cite{Kamp2010,Kamp2015,Hepburn1973}.

	In general, impact-prone areas and exaggerated structures, such as horns and legs exhibit cuticle organization that resists deformation and fracture.
	Acorn weevils in the genus \textit{Curculio} are typified by an elongate structure of the head, called the rostrum (snout), which instead exhibits unusual distal flexibility.
	The rostrum is a hollow, strongly curved (over 90$\degree$ in some species), cylindrical, exoskeletal extension of the otherwise nearly-spherical head, which bears at its apex the terminal chewing mouthparts.
	Despite being composed of the same material as other rigid body parts, the snout can be repeatedly bent without evident damage.
	This structure is used by the female to feed and excavate sites for egg-laying (oviposition); the latter process causes significant, apparently elastic, deformation of the rostrum\improvement{as illustrated in figure 1c}.
	By maintaining constant tension on the snout and rotating around the bore-hole, females are able to flex the rostrum into a near-perfectly straight configuration and thereby produce a linear channel into the fruit; a single female may prepare hundreds of such sites during the adult stage.

@@

	We additionally describe the fracture mechanics of the snout, as pertains to both cuticle composite structure and tensile behavior, and consider how modification of the cuticle may reduce the risk of rostral fracture during oviposition.
	Based on our findings we posit that the composite profile of the rostral apex enables the snout to be flexed until straight while remaining within the elastic limits of the material, mitigating the risk of structural damage, and without evident alteration of the mechanical properties of the individual components of the cuticle across the structure and between species.
	Thus, the flexibility and tensile strength of the rostrum appear to be derived \emph{exclusively} from modification of the composite architecture of the exoskeleton.
	To our knowledge, this is the first time that a modified composite profile has been reported as a means of enhancing structural elasticity in the insect exoskeleton.
}	
	\section{Microstructure of the \textit{Curculio} rostrum}
	\info{850 words, reduce in revisions}
		In arthropods (including beetles), the exocuticle is comprised of numerous unidirectional laminae of chitin fibers; each layer is the thickness of a single fiber (2-4\,nm) embedded in a proteinaceous matrix.
		These layers are stacked at a more or less constant angle to each other, thus forming a quasi-isotropic laminate referred to as the Bouligand structure \cite{Blackwell1980,Bouligand1972,Neville1976}. 
		This layout effectively produces a transversely isotropic composite, mitigating the strong anisotropy of \textalpha-chitin to yield a versatile building material for the exoskeleton.

@@

	\section{Force-controlled loading to fracture}
	%550 words, maybe reduce?? Still must add numbers...

		To better characterize the mechanical behavior of the snout as an integrated whole, we performed tensile testing on the snouts of six species in the genus \textit{Curculio}, representing a mixture of closely and distantly related taxa.
		Although the heads were rehydrated by immersion in de-ionized water for 24 hours, we observed comparatively brittle fracture (but see below), in contrast to GIVE EXAMPLES HERE.

		In general, the behavior of the rostrum is non-linear viscoelastic, and, as in other biological materials, exhibits a stress-strain curve characterized by a steady increase in stiffness, beginning with a toe-in region and terminating in apparently brittle fracture after a period of strain hardening.
		We observed that the maximum force sustained at the site of the break was strongly correlated with the cross-sectional area of the endocuticle, and not the exocuticle.
		Consequently, there was a negative correlation between utlimate tensile strength of the specimen and the ratio of exocuticle to endocuticle cross-sectional area at the site of fracture.
		In other words, UTS is positively correlated with the relative proportion of the endocuticle across species.

		Although the proportion of exocuticle is predicted to be positively correlated with the stiffness of the resulting composite, we found no such associations because of the anterior-posterior gradient in cuticle profile.
		Because the cross-sectional areas of the cuticle regions vary across the length of the head, it is meaningless to attempt to correlate these areas to properties of the entire snout.
		Instead, we found that the uniaxial elastic moduli of the snout under low strain (E-low) was inversely correlated with the ultimate strain and toughness of the snout (as was the secant modulus, E-sec).
		These associations were found to be statistically significant and independent of species membership, rostrum length, and location on the snout.

		From our results, we infer that there is little variation in the gross elastic behavior of the cuticle across the genus, in agreement with our current understanding of cuticle mechanobiology, making it unlikely that differences in sclerotization or chitin composition within the cuticle are responsible for the mechanical behavior of the rostrum (singh 2016, jansen 2016).
		Furthermore, the endocuticle apparently contributes more to the tensile strength of the rostrum than the exocuticle, likely because the endocuticle is organized in large bundles of aligned, anisotropic fibers.
		Thus, in addition to making the cuticle more flexible, the altered apical composite profile makes the rostrum less likely to break, suggesting a possible means by which this system evolved\info{(via negative selection of breakage, maybe say this in conclusions)}.

		\info{DO I really want to discuss this? Occupies precious space...}Finally, we observed that the elastic modulus is higher in specimens with a longer snout.
		This observation was initially quite puzzling, as we had expected that a longer (and typically more strongly curved [insert ecomorph paper ref here]) would need to be more flexible to avoid fracture during oviposition.
		Based on preliminary confocal microscopy data, we speculate that this may be the result of a longer transition gradient from the basal profile to the apical profile in longer rostra.
		A decrease in exocuticle thickness along a longer portion of the base might reinforce the snout against buckling; however Young's modulus of the rostrum would be comparatively higher in these species because of the greater volume fraction of exocuticle.

	\section{Load cycling of \textit{Curculio caryae}}
	%375 words, add no more than 100, ONLY IF NEEDED
		The shearing motion and accommodation of strain led us to question how the cuticle might accommodate repeated strain, as is seen in the living organism.
		We therefore performed fatigue testing on a female curculio longinasus, which exhibits the most extreme degree of bending in the sis species examined.

		~400K cycles, complete elongation, rehydrated, coated in grease to prevent loss of moisture and stiffening of the specimen.
		We observed viscoelastic behavior in the specimen, as indicated by histeresis in the stress-strain relationship during each cycle.
		Fmax decreased logarithmically with cycle number, etc., and the specimen appeared to have deformed plastically during the test.
		We initially believed that this indicated damage to the specimen; however, after cleaning the specimen in a 24 hour wash with ethanol and water, we observed that the specimen returned to its original shape.
		The specimen did not show any evidence of fractures or shear cusps anywhere in the surface of the exocuticle, and, furthermore, the tensile strength of the specimen was consistent with other members of its species.
		Given this surprising result, it appears that the specimen was undamaged by the testing.
		We therefore believe that under normal conditions in life, repeated bending of the snout does exceed the yield/plastic limit of the cuticle, and the bending strain is purely elastic/viscoelastic.

		We cannot fully account for these results, but we speculate that the microstructure of the endocuticle is responsible for what we observed.
		The endocuticle is made of aligned \textalpha-chitin nanofibrils whose crystalline structure is enforced by hydrogen bonds between individual chitin chains along their length.
		The viscoelasticity of the cuticle is thought, in part, to come from slippage between these chains as the hydrogen bonds break and reform in response to shearing between the chitin molecules.
		We believe that repeated strain may have caused such slippage in the endocuticle of the rostral apex during the fatigue test, but without sufficient time for the material to \textit{completely} relax after deformation, the specimen would slowly accumulate strain and consequently deform viscoelastically/viscoplastically.
		After 24 hours soaking in ethanol and water, the hydrogen bonds would relax sufficiently to allow the specimen to return to its original configuration, dissipating the accumulated strain without any damage to the specimen.

	\section{Fractography of test specimens}
	%currently ~400 words, keep to this length or reduce to 2 short paragraphs
		Examination of the fracture surfaces and adjacent cuticle of tensile testing specimens revealed that although fracture was comparatively brittle, the fracture mechanics of the exocuticle and endocuticle differed according to their microstructure, in agreement with previous studies (name some).

		In cross-section, the exocuticle consistently presented a smooth, nearly continuous fracture surface, indicative of relatively brittle fracture, likely due to the microarchitecture and resultant transverse isotropy of the Bouligand structure (explain this).
		Endocuticle, on the other hand exhibited severe delamination, ply-splitting, and fiber pulling, consistent with viscoelastic/plastic behavior shown in previous studies and congruent with theoretical consideration of the microstructure of this material (name something here). 
		These patterns indicate that the endocuticle is probably less brittle than the exocuticle, most likely due to the alignment of the \textalpha-chitin fibers in each macrofiber.

		In addition, the exocuticle typically appears to fracture before the endocuticle, with shear-cusp formation evident over unbroken endocuticle.
		We note, however, that the exocuticle of weevils/beetles is anchored to the endocuticle by cross-linking fibers in a transition zone described by Kamp et al. (see refs.).
		The presence of shear-cusps therefore indicates that the fibers of the endocuticle are shearing past each other within each ply along the radial/normal plane (type II shearing???, extension shear-coupling).
		Furthermore, given the delamination observed between plies, the layers of endocuticle are likely shearing past each other (type III shearing) along the transverse plane.
		We therefore infer that, under tension, the endocuticle tends to deform viscoelastically and plastically along the longitudinal axes of the macrofibers, while the overlying exocuticle exhibits brittle fracture due to shearing between the stretching endocuticle fibers to which it is anchored.

		Additionally, the fracture surfaces show a characteristic failure mode, based on the pattern of fiber dislocation in the plies of the endocuticle.
		(copy description from DATA PRESENTATION, for figure 5B).

		From this pattern we hypothesize that the exocuticle-rich gular sutures are the most likely site for the initiation of void nucleation and failure of the integrated rostral cuticle in cross section.
		Structural failure would take place as cracks propagate through the endocuticle from these sutures, which penetrate the entire thickness of the laminate.
		We speculate that this could be the reason why the cross-sectional profile of \textit{C. caryae} is flattened ventrally.
		Flattening this region may reduce tensile-strain across the gular sutures when the snout is bent dorsally, thus reducing the risk of fracture in the elongate, strongly-curved rostrum in this species.

	\section{Conclusions}
	%1-2 'short paragraphs', 300 words maximum

@@

		\subsection*{Specimen imaging and microscopy}

>>>>

%This study demonstrates: (1) there are 2 microstructural modifications to the composite profile of the cuticle of the rostral apex that would enhance cuticular flexibility, present in all examined species, and likely across the genus (2) thickness of the encocuticle is directly proportional to the maximum tensile force sustained in tension, to the exclusion of the exocuticle, (3) the tensile strenth of the snout varies across the length of the head and is inversely proportional to exo/endocuticle ratio, such that the more flexible areas are also stronger under tension, (4) young's modulus is higher for longer snouts, reflecting increased reinforcement at the base of the snout, likely to prevent bucking fracture at the base, (5) because of the modifications to the cuticle of the rostral apex (which result in all of these changes to the mechanical properties of the snout), bending appears to be viscoelastic/elastic, with a relatively low risk of breakage during the lifetime of the beetle, (6) when the rostrum does fail, crack initiation appears to take place in the exocuticle-rich occipital sulci, which would be under tension during the drilling behavior in the live insect.

@@

%-------------------------------------------------------------------------------
%introduction - nature materials requires that introduction is given NO SECTION HEADER, 500 words
}

\section*{Introduction} \info{670 words, reduce to 600 or less in revisions, structure of argument/narrative is good}
%Intro - 670 words, reduce to 500 or so
	{The exoskeleton of Coleoptera (beetles) is a hierarchically-structured fibrous composite characterized by variously arranged \textalpha-chitin (N-acetylglucosamine) nanofibrils embedded in a heterogeneous protein matrix.
	Although \textalpha-chitin is brittle and strongly anisotropic\unsure{give some numbers here}, beetle cuticle is simultaneously rigid and tough due to its unique laminate microstructure\unsure{give more numbers here}.
	Beetle cuticle is divided into two structurally and mechanically distinct regions, the (outer) exocuticle and (inner) endocuticle.
	The exocuticle is characterized by a transversely-isotropic helicoidal structure that is comparatively rigid (though brittle) and has been the subject of numerous prior studies\unsure{numbers and refs}.
	By contrast, the endocuticle of beetles is comprised of large, aligned bundles (macrofibers) of chitin that are strongly anisotropic\unsure{numbers again}.
	Arranged in unidirectional laminae, the macrofibers improve cuticle toughness by inhibiting crack formation and propagation between successive plies \cite{Kamp2010,Kamp2015,Hepburn1973}.

	In general, impact-prone areas and exaggerated structures, such as horns and legs exhibit cuticle organization that resists deformation and fracture.
	Acorn weevils in the genus \textit{Curculio} are typified by an elongate structure of the head, called the rostrum (snout), which instead exhibits unusual distal flexibility.
	The rostrum is a hollow, strongly curved (over 90$\degree$ in some species), cylindrical, exoskeletal extension of the otherwise nearly-spherical head, which bears at its apex the terminal chewing mouthparts.
	Despite being composed of the same material as other rigid body parts, the snout can be repeatedly bent without evident damage.
	This structure is used by the female to feed and to excavate sites for egg-laying (oviposition); the latter process causes significant, apparently elastic, deformation of the rostrum\improvement{as illustrated in figure 1c}.
	By maintaining constant tension on the snout and rotating around the bore-hole, females are able to flex the rostrum into a near-perfectly straight configuration and thereby produce a linear channel into the fruit; a single female may prepare hundreds of such sites during the adult stage.

@@

	We additionally describe the fracture mechanics of the snout, as pertains to both cuticle composite structure and tensile behavior, and consider how modification of the cuticle may reduce the risk of rostral fracture during oviposition.
	Based on our findings, we posit that the composite profile of the rostral apex enables the snout to be flexed until straight while remaining within the elastic limits of the material, mitigating the risk of structural damage, and without evident alteration of the mechanical properties of the individual components of the cuticle across the structure and between species.
	Thus, the flexibility and tensile strength of the rostrum appear to be derived \emph{exclusively} from modification of the composite architecture of the exoskeleton.
	To our knowledge, this is the first time that a modified composite profile has been reported as a means of enhancing structural elasticity in the insect exoskeleton.
}	
	\section{Microstructure of the \textit{Curculio} rostrum}
	\info{780 words, reduce in revisions}
		In arthropods (including beetles), the exocuticle is comprised of numerous unidirectional laminae of chitin fibers; each layer is the thickness of a single fiber (2-4\,nm) embedded in a proteinaceous matrix.
		These layers are stacked at a more or less constant angle to each other, thus forming a quasi-isotropic laminate referred to as the Bouligand structure \cite{Blackwell1980,Bouligand1972,Neville1976}. 
		This layout effectively produces a transversely isotropic composite, mitigating the strong anisotropy of \textalpha-chitin to yield a versatile building material for the exoskeleton.

@@

	\section{Force-controlled loading to fracture}
	%600 words... still must add numbers...

		To better characterize the mechanical behavior of the rostrum at failure, we performed tensile testing on the snouts of six \textit{Curculio} species, representing a mixture of closely and distantly related taxa.
		Heads of female specimens of each species were rehydrated by immersion in de-ionized water for 24 hours
		Each specimen was subjected to force-controlled, uniaxial loading to fracture at a constant stress rate (detailed in Methods).
		We then examined the correspondence between composite structure and mechanical behavior of the snout, using phylogenetic linear mixed effects models to account for phylogenetic non-independence in the residual variances of the models.

		In general, the specimens exhibited a non-linear viscoelastic response curve characterized by a sharp increase in stress at higher strains, terminating in apparently brittle fracture after a period of strain hardening.
		We observed that the maximum force sustained at the site of the break was strongly correlated with the cross-sectional area of the endocuticle, and not the exocuticle, at that site.
		Consequently, there was a negative correlation between ultimate tensile strength of the specimen and the ratio of exocuticle to endocuticle cross-sectional area at the site of fracture.
		Inversely, the failure strength of the cuticle is positively associated with the relative proportion of the endocuticle.

		Although CLPT predicts that the proportion of exocuticle is positively correlated with the stiffness of generalized cuticle, we found no associations between the cross-sectional properties of the fracture site and the gross behavior of the entire rostrum.
		Because the cross-sectional areas of the cuticle regions vary across the length of the head along an anterior-posterior gradient, it is not possible to correlate measurements from the fracture surface to the properties of the entire snout.
		Instead, we found that the uniaxial elastic modulus of the snout under low strain (E-low) was inversely correlated with the ultimate strain and toughness of the snout (as was the secant modulus, E-sec)
		These associations were all found to be statistically significant and independent of species membership.

		Additionally, we observed a moderate stiffening size-effect with respect to rostral length.
		This observation was initially quite puzzling, as we had expected that a longer (and typically more strongly curved [insert ecomorph paper ref here]) snout would need to be more flexible to avoid fracture during oviposition.
		Based on preliminary confocal microscopy data, we speculate that this may be the result of a longer transition gradient from the basal profile to the apical profile in longer rostra.
		We hypothesize that a decrease in exocuticle thickness along a longer portion of the base might reinforce the snout against buckling; however Young's modulus of the rostrum would be comparatively higher in these species because of the greater volume fraction of exocuticle.

		From these results, we infer that the gross elastic behavior of the cuticle is consistent across the genus, in agreement with our current understanding of cuticle mechanobiology.
		It is therefore unlikely that differences in sclerotization or chitin composition within the cuticle, rather than composite profile, are responsible for the mechanical behavior of the rostrum in different species.
		Furthermore, the endocuticle apparently contributes more to the tensile strength of the rostrum than the exocuticle, likely because the endocuticle is organized in large bundles of aligned, anisotropic fibers.
		Thus, the altered composite profile of the cuticle in the rostral apex makes the rostrum simultaneously more flexible and fracture resistant.

	\section{Load cycling of \textit{Curculio caryae}}
	%480 words
		To confirm that repeated, proscribed straightening of the rostrum does not result in damage to the cuticle, we performed displacement-controlled fatigue testing on a typical female specimen of \textit{Curculio caryae}, a species that exhibits extreme ($80-90\degree$) rostral curvature.
		The head was removed and rehydrated for 24 hours in de-ionized water, then coated in grease to prevent loss of moisture and stiffening of the specimen during the duration of the test.
		The specimen was then aligned so that uniaxial tension would induce elongation of the apical portion of the rostrum.
		The strain per cycle was fixed at an amplitude sufficient to completely elongate the snout and generate a tensile load equal to $0.2\times$ the average tensile strength of conspecifics in the straightened configuration, at a frequency of $0.33\,\text{Hz}$.
		The test was terminated after a period of two weeks (ca.~400K cycles) when the strain amplitude appeared to reach an asymptotic minimum.

		We observed viscoelastic behavior in the rostrum, as indicated by histeresis in the stress-strain relationship during each cycle.
		Strain amplitude decreased logarithmically with cycle number, and the specimen initially appeared to have deformed plastically during the test.
		We believed that this indicated damage to the specimen; however, after cleaning the specimen in a 24 hour wash with ethanol and water, we observed that rostrum returned to its original shape.

		We cannot fully account for the stress relaxation of the rostrum after testing, but we speculate that it arose from the same mechanism as the viscoelastic behavior observed in tensile testing.
		The endocuticle is made of aligned \textalpha-chitin nanofibrils whose crystalline structure is enforced by hydrogen bonds between individual chitin chains along their length.
		The viscoelasticity of the cuticle is thought, in part, to come from slippage between these chains as the hydrogen bonds break and reform in response to shearing between the chitin molecules.
		We believe that repeated strain may have caused such slippage in the endocuticle of the rostral apex during the fatigue test; however, without sufficient time for the material to \textit{completely} relax after deformation, the specimen would slowly accumulate strain and consequently deform viscoelastically (REF\info{stress history dependence paper}).
		After 24 hours soaking in ethanol and water, the hydrogen bonds would relax sufficiently to allow the specimen to return to its original configuration, dissipating the accumulated strain.

		The specimen did not show any evidence of fractures, micro-tears, or shear cusps anywhere in the surface of the exocuticle, and, furthermore, the tensile strength of the specimen was consistent with other members of its species ($F_max~=~5.02\,\text{N}$).
		Given this surprising result, it appears that the specimen was undamaged by the testing.
		We therefore expect that under normal conditions in life, repeated bending of the snout does not exceed the yield strength of the cuticle, and the bending strain is purely elastic.

	\section{Fractography of test specimens}
	%currently ~650 words
		Due to the complex failure patterns present across the fracture surface, it was not always possible to identify void nucleation and crack initiation sites (both primary and secondary).
		Nonetheless, we observed several patterns characteristic of both the micro-scale behavior of the cuticle and the meso-scale behavior of the rostrum during uniaxial tensile failure, which we describe here.

		Scanning electron and light microscopy of testing specimens revealed that the fracture mechanics of the exocuticle and endocuticle differed according to their microstructure.	
		In transverse view, the exocuticle consistently presented a nearly continuous fracture surface, indicative of comparatively brittle failure, likely due to the helicoidal arrangement of \textalpha-chitin laminae and resultant transverse isotropy of the Bouligand structure.
		The exocuticle typically appeared to fracture at lower strains than the endocuticle, with shear-cusp formation evident across the fracture surface and over unbroken endocuticle on the rostral surface adjacent to the plane of fracture.
		Conversely, the endocuticle exhibited severe delamination, off-axis ply-splitting, and fiber-pulling away from the fracture surface, indicating that endocuticular macrofibers are less brittle than the exocuticle due to the unidirectional alignment of their \textalpha-chitin fibers.
		Because the exocuticle of weevils is anchored to the endocuticle by cross-linking fibers, the presence of exocuticular shear-cusp formation in uniaxial tension suggests extension-shear coupling within individual endocuticle laminae, which caused ply-splitting via mode II fracture between macrofibers at high strain.
		This intra-laminar extension-shear coupling also yielded off-axis in-plane resultant forces as a function of lamina orientation angle; mode III shearing then occurred between laminae with opposing in-plane resultant forces, causing inter-ply delamination.
		Tensile failure of the macrofiber laminae would ultimately occur via mixed-mode I/II (transverse tension/intra-laminar shear) fracture due to an increase in applied stress caused by ply-splitting in adjacent laminae.

		At the meso-scale, most specimens fractured along a single plane across and between the occipital sulci, which are cuticle invaginations that traverse the entire length of the rostrum.
		These sulci increase the volume fraction of exocuticle in the ventral part of the snout and create large interfaces ideal for void nucleation.
		The exocuticle of the occipital sulci usually displayed shear cusps oriented outward from the center of the invagination, continuing dorsolaterally and ventromedially.
		Ventrally the cusps converged toward a prominent scarp where the crack fronts joined, although in specimens with large cross-sectional areas of endocuticle, this was often obscured by delaminated endocuticular macrofibers.

		The first layer of endocuticle usually fractured along the same plane as the exocuticle, and ventrally the endocuticle laminae typically converged toward a scarp-like region characterized by severe delamination and numerous de-bonded macrofibers.
		Additionally, macrofibers oriented in the direction of crack propagation exhibited extensive ply-splitting with intermittent transverse shearing, while macrofibers oriented against the direction of crack propagation primarily displayed fracture by transverse shear along the plane of ply-splitting in adjacent laminae.
		Thus, contralateral fibers in the same lamina displayed opposing fracture modes.
		In addition, the ventrolateral surfaces often exhibited extensive inter-ply delamination and fiber de-bonding in scarp-like prominences, likely due to a combination of tensile failure and shearing along the dorsally-radiating crack front.
		Dorsally, the coalescent crack fronts often caused significant de-bonding and ply-splitting followed by broom-like tensile failure; in some specimens, the contralateral crack fronts were out of plane and coalesced via transverse shearing through a large dorsal section of cuticle.

		From these patterns we hypothesize that the exocuticle-rich occipital sulci are the most likely site for the initiation of void nucleation and catastrophic failure of the integrated rostral cuticle in cross section, as illustrated in Fig~REF.
		According to this model, structural failure would take place as cracks propagate through the endocuticle from these sutures, which penetrate the entire thickness of the laminate.
		Although other, more complex failure modes have been observed, we posit that in live specimens this is the most likely mechanism of tensile failure because typical bending behavior generates tension along the ventral surface of the rostrum.

	\section{Conclusions}
	%1-2 'short paragraphs', 300 words maximum, already at 3200...
		In this study, we...
		raising the intriguing possibility that this system evolved via negative selection of breakage, rather than positive selection of flexibility.\info{(maybe say this in conclusions)}

		evolutionary constraint (like occipital sulci)

		The macrofibers are pulled longitudinal axis, explains fmax, toughness, and upcurved stress-strain curve.

		We therefore infer that, under uniaxial tension, the endocuticle deforms viscoelastically along the longitudinal axes of the macrofibers, causing ply-splitting and delamination at high strain, while the overlying exocuticle exhibits brittle fracture, at a comparatively low strain, due to shearing between the stretching endocuticle fibers to which it is anchored.
		This outcome is consistent with behavior shown in previous studies and is congruent with theoretical consideration of cuticle microstructure in CLPT, which predicts extension shear-coupling ($A_{16}, A_{26}\neq{0}$) for individual off-axis macrofiber laminae.

@@

		\subsection*{Specimen imaging and microscopy}
			Cold-fracture of rostra
